Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-22 prob.tex
prob.tex Updates here and there...

It is common to consider convex interval-valued probability measures.
For example, a special case of convex interval-valued probability
measures consists the Dempster-Shafer belief function as the left-end
and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
Dempster-Shafer functions, also called \emph{completely or totally
monotone}, plays an important role in the theory of non-additive belief.
Furthermore, convex interval-valued probability measures have a good
property that they can always be associated with real-valued probability
measures.

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]\label{thm:Shapley}
Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}

\yutsung{Because the physical meaning of convex is still not clear,
it would be better if we can find or prove a theorem which removes
``convex'' in the theorem. However, I still have not found an example
with an empty core or a real-valued probability measure in the core
of each interval-valued probability measure. What we know:
\begin{enumerate}
\item The cloud in \cite{JamisonLodwick2004} cannot induce an interval-valued
probability measure. Therefore, any results related to clouds cannot
be used directly.
\item The definition of interval-valued probability measure in \cite{JamisonLodwick2004}
is different from any later definition of interval-valued probability
measure written by Lodwick, including \cite{Lodwick2008}.
\item About linear programming, the Mathematica program solving the case
$\left|\Omega\right|=1$ or $2$ gives positive answer. The program
ceases to respond when outputting $\left|\Omega\right|=3$. Maybe
I should simplify the program?
\item Check whether the Shapley value still in the core or not in our setting...?
\end{enumerate}
}

@@

@@

\begin{figure}[t]
\[
\begin{array}{c}
\hspace{1cm}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix@R=0.9em{ & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd]\\
\lstick{\bar{\mu}} & \qw & \ctrl{1} & \qw & \gate{H} & \qw & \meter & \cw & \cw & \control\cw\\
 & \qw & \targ & \qw & \qw & \qw & \meter & \cw & \control\cw & \cwx & \ar@{.}[dd]\\
 & \qw & \qw & \qw & \qw & \qw & \qw & \qw & \gate{X}\cwx & \gate{Z}\cwx & \qw\\
 & \push{\bar{\mu}_{0}} &  & \push{\bar{\mu}_{1}} &  & \push{\bar{\mu}_{2}} &  & \push{\bar{\mu}_{3}} &  &  & \push{\bar{\mu}_{4}}
}
\end{array}
\]
\caption{Circuit for Quantum Teleportation}

\label{fig:QuantumTeleportation} 
\end{figure}

>>>>

It is common to consider convex interval-valued probability measures.
For example, a special case of convex interval-valued probability
measures consists the Dempster-Shafer belief function as the left-end
and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
Dempster-Shafer functions, also called \emph{completely} or \emph{totally
monotone}, plays an important role in the theory of non-additive belief.
Furthermore, convex interval-valued probability measures have a good
property that they can always be associated with real-valued probability
measures.

\begin{thm}{[}Shapley~\cite{Shapley1965,GilboaSchmeidler1994}{]}\label{thm:Shapley}
Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}

\yutsung{Because the physical meaning of convex is still not clear,
it would be better if we can find or prove a theorem which removes
``convex'' in the theorem. However, I still have not found an interval-valued
probability measure with an empty core or proved that each interval-valued
probability measure has an nonempty core. What we know:
\begin{enumerate}
\item The cloud in \cite{JamisonLodwick2004} cannot induce an interval-valued
probability measure. Therefore, any results related to clouds cannot
be used directly.
\item The definition of interval-valued probability measure in \cite{JamisonLodwick2004}
is different from any later definition of interval-valued probability
measure written by Lodwick, including \cite{Lodwick2008}.
\item About linear programming, the answer of Mathematica program for $\left|\Omega\right|=3$
is too complex to read by human. May need to simplify the result to
a human readable one?
\item Check whether the Shapley value still in the core or not in our setting...?
\end{enumerate}
}

@@

\[
\left(\bar{\mu}_{1}\otimes\bar{\mu}_{2}\right)\left(P_{1}\otimes P_{2}\right)=\bar{\mu}_{1}\left(P_{1}\right)\bar{\mu}_{2}\left(P_{2}\right)?
\]
Is $\bar{\mu}_{1}\otimes\bar{\mu}_{2}$ still a quantum interval-valued
probability measure?

Might be hard, because let $\mu\otimes\mu$ is not a quantum real-valued
probability measure, where $\mu$ is a non-Born real-valued probability
measure for dimension 2.

@@

\begin{figure}[t]
\[
\begin{array}{c}
\hspace{1cm}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix@R=0.9em{ & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd]\\
\lstick{\bar{\mu}} & \qw & \ctrl{1} & \qw & \gate{H} & \qw & \meter & \cw & \cw & \control\cw\\
 & \qw & \targ & \qw & \qw & \qw & \meter & \cw & \control\cw & \cwx & \ar@{.}[dd]\\
 & \qw & \qw & \qw & \qw & \qw & \qw & \qw & \gate{X}\cwx & \gate{Z}\cwx & \qw\\
 & \push{\bar{\mu}_{0}} &  & \push{\bar{\mu}_{1}} &  & \push{\bar{\mu}_{2}} &  & \push{\bar{\mu}_{3}} &  &  & \push{\bar{\mu}_{4}}
}
\end{array}
\]
\caption{\label{fig:QuantumTeleportation}Circuit for Quantum Teleportation}
\end{figure}

In figure~\ref{fig:QuantumTeleportation}, let $\ket{\phi}=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{11}\right)$.

$\bar{\mu}_{0}=\bar{\mu}_{1}\otimes\mu_{\ket{\phi}}^{B}$. Notice
that a quantum real-valued probability measure can be considered as
an special case of quantum interval-valued probability measure.
